### 2021-02-10 input/proposal.tex
wip
rewrite algo, todo test it

@@

The main idea is maintaining graphs of partitions using local
knowledge only and use graphs as often as possible: it improves
resilience to crashes, convergence speed etc. Unfortunately,
maintaining graphs of partitions in dynamic networks may require the
use of broadcast tree. The removal of a communication channel between
2 processes may remove an advantageous path from processes downstream
to the source of the partition they belong to.

@@

@@

\paragraph{Static network with dynamic partitions.}
At any time, a source can revoke its self-appointed status of source,
hence \TODO{removing} its partition of the system. All processes that
belong to this partition must choose another partition to belong to.
To handle dynamic partitions, processes require two additional
components.

\noindent \textbf{First,} since the number of partitions does not
monotonically increase in the system any longer, they require a vector
of versions that monotonically increases over \TODO{add and del}
operations. This allows processes to quickly discard stale messages
saving bandwidth. For instance, a process that received a message
originated at Process $a$ with a version $2$ knows that any message
originated at Process $a$ with a version $1$ are stale system-wide; it
must not forward it. As consequence, vectors of versions also ensure
termination, for messages \TODO{add and del} cannot follow each other
in an infinite loop. In terms of traffic, this only requires each
\TODO{delete} message to piggyback a source identifier and version
number.

\noindent \textbf{Second,} processes need to maintain a local view of
their neighbors' partition.  Figure~\ref{fig:del} shows that
\TODO{deletes} may not propagate properly to all processes in
need. The path leading to processes delivering $add$ may be broken due
to concurrent deliveries.  To solve this issue, each process is able
to know with certainty that each of its neighbor does not need a
delete (either because it is in another partition, or because another
path exists from the source to this neighbor). \TODO{More, figures
  etc.} In terms of traffic, this requires to acknowledge each message
in a way or another (acknowledgement messages or included in each
add-del message) using FIFO communication channels. The propagation of
delete messages is limited to the partition it targets plus uncertain
processes.

\noindent \textbf{Finally,} the delete must trigger another
competition amongst neighboring partitions. These \TODO{add}
messages operate normally and fill gaps left open by deletes.

>>>>

\TODO{Remember to say stateless, asynchronous system.}

@@

Each process works autonomously and each change is broadcast to its
neighborhood, for neighbors may depend on this change as well.

% The main idea is maintaining graphs of partitions using local
% knowledge only and use graphs as often as possible: it improves
% resilience to crashes, convergence speed etc. Unfortunately,
% maintaining graphs of partitions in dynamic networks may require the
% use of broadcast tree. The removal of a communication channel between
% 2 processes may remove an advantageous path from processes downstream
% to the source of the partition they belong to.

@@

\begin{algorithm}
  \input{input/algoadddelundo.tex}
  \caption{\label{algo:adddelundo}Dynamic partitioning by Process $p$.}
\end{algorithm}

@@

\paragraph{Static network with dynamic partitions.}
At any time, a source can revoke its self-appointed status of source,
hence \TODO{removing} its partition of the system. All processes that
belong to this partition must choose another partition to belong to.

\noindent Since the number of partitions does not monotonically
increase in the system any longer, they require a vector of versions
that monotonically increases over \TODO{add and del} operations. This
allows processes to quickly discard stale messages saving
bandwidth. For instance, a process that received a message originated
at Process $a$ with a version $2$ knows that any message originated at
Process $a$ with a version $1$ are stale system-wide; it must not
forward it. As consequence, vectors of versions also ensure
termination, for messages \TODO{add and del} cannot follow each other
in an infinite loop. In terms of traffic, this only requires each
\TODO{delete} message to piggyback a source identifier and version
number.

% \noindent \textbf{Second,} processes need to maintain a local view of
% their neighbors' partition.  Figure~\ref{fig:del} shows that
% \TODO{deletes} may not propagate properly to all processes in
% need. The path leading to processes delivering $add$ may be broken due
% to concurrent deliveries.  To solve this issue, each process is able
% to know with certainty that each of its neighbor does not need a
% delete (either because it is in another partition, or because another
% path exists from the source to this neighbor). \TODO{More, figures
%   etc.} In terms of traffic, this requires to acknowledge each message
% in a way or another (acknowledgement messages or included in each
% add-del message) using FIFO communication channels. The propagation of
% delete messages is limited to the partition it targets plus uncertain
% processes.

\noindent Deletes must trigger competition amongst neighboring
partitions. These \TODO{add} messages operate normally and fill gaps
left open by deletes.
